Titeln på avhandlingens språk

### 2022-11-06 sampling.tex
Update on Overleaf.

Now, we modify the problem (see section \ref{sec:aprxSol_Energy_samples}) and find the optimum sampling instants that minimises the expected number of samples for a given upper bound for the expected wait time. First note that, the general solution has constants $\alpha$ and $\beta$ that corresponds to the weights given to the cost of sampling and cost of waiting, respectively. The optimisation criteria changes from minimising wait time to minimising the number of samples, when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity. As any positive real value is valid for this ratio, we can argue that any optimisation problem -- constrained or unconstrained -- can be boiled down to thewith all possible real values in between

>>>>

Now, we modify the problem (see section \ref{sec:aprxSol_Energy_samples}) and find the optimum sampling instants that minimises the expected number of samples for a given upper bound for the expected wait time. First note that, the general solution has constants $\alpha$ and $\beta$ that corresponds to the weights given to the cost of sampling and cost of waiting, respectively. The optimisation criteria changes from minimising wait time to minimising the number of samples, when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity. As any positive real value is valid for this ratio, we can argue that any optimisation problem -- constrained or unconstrained -- can be boiled down to modwith all possible real values in between
